Cell Decompositions for Rank Two Quiver Grassmannians

### 2018-03-16 Grassmannian_cells.tex
Added corollary on openness and a say about cell decompositions

@@

\begin{theorem}
  \label{cellscover}
  For $m\geq 1$ and $I\subsetneq\{1,\ldots,n\}$, every quiver Grassmannian $\Gr^{\tilde Q}_\tbfe(\tilde P_{m+1}^I)$ admits a cell decomposition into affine spaces.
\end{theorem}
\begin{proof}
  We work by induction on $m$.
  When $m=1$, the claim is trivial since in this case all quiver Grassmannians are points.
  We establish the result for $m\ge2$ by proving the following more general statement:\bigskip

@@

>>>>

\begin{corollary}
  The image of $\Psi_{m+1,I,j}$ is open for all $\tbfe$, $\tbff$, and $\tbfg$.
\end{corollary}

@@

\begin{theorem}
  \label{cellscover}
  For $m\geq 1$ and $I\subsetneq\{1,\ldots,n\}$, every quiver Grassmannian $\Gr^{\tilde Q}_\tbfe(\tilde P_{m+1}^I)$ admits a cell decomposition.
\end{theorem}
\begin{proof}
  We work by induction on $m$.
  When $m=1$, the claim is trivial since in this case all quiver Grassmannians are points.
  We establish the result for $m\ge2$ by proving the following more general statement:\bigskip

@@

  \sayD{When $\Psi_{m+1,I,j}$ is surjective, $\cG_{\tbff,\tbfg}$ is a closed subset of the Grassmannian.
  The map is not surjective exactly when $\tbfg=\udim \tilde P_{m+1}^I$ and so we get a cell decomposition by taking the affine cells from this $\cG_{\tbff,\tbfg}$ last.}
